%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=.8, top=1.5cm, bottom=1.5cm]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
% 
%\firstname{Lingwei} % Your first name
%\familyname{Kong} % Your last name
\firstname{Lingwei} % Your first name
\familyname{Kong} % Your last name

%\title{Lingwei Kong}
% All information in this block is optional, comment out any lines you don't need

%\address{B Block,Sector 62}{Noida, UP}
\address{University of Amsterdam \& Tinbergen Institute\\ \emailsymbol \emaillink{l.kong@uva.nl}~~\emailsymbol \emaillink{lingweik6@gmail.com} \\ }{}
\homepage{sites.google.com/view/lingwei-kong}{My Site: http://sites.google.com/view/lingwei-kong} 
%\mobile{(+31) 685438594}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
%\email{l.kong@uva.nl}
% The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
 % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-5mm}
{\color{color2!50}\rule{\textwidth}{.25ex}}%
\vspace{3mm}
%\cventry{\textbf{}}{}{}{}{}{}  \vspace{-1mm}
\cventry{\href{https://www.tinbergen.nl/job-market-career-perspectives}{{Tinbergen} {Institute}}}{\textbf{Placement Director}}{}{}{}{\textnormal{Professor Eric (E.J.) Bartelsman, \emailsymbol \emaillink{e.j.bartelsman@vu.nl}~~ {\emailsymbol \emaillink{eric.bartelsman@vu.nl} }~~\mobilesymbol{+31 (0)20 598 6167/4590}}}  
\cventry{}{\textbf{Placement Assistants}}{}{}{}{\textnormal{Arianne de Jong,~~~\emailsymbol \emaillink{a.de.jong@tinbergen.nl} \\ Christina M\'{a}nsson, \emailsymbol \emaillink{c.mansson@tinbergen.nl}}}    

{\color{color2!50}\rule{\textwidth}{.25ex}}%

%\cventry{Dec 2017 --
%	Oct 2018}{Activity Head of marketing}{\textsc{RDV,18 -IIT Delhi}}{}{New Delhi}{\textnormal{Created the social campaigns by leading 5 members of team head for marketing of biggest north Indian cultural fest(RDV). Pitched companies for sponsorship, Designed and managed their marketing event and stalls collaborating with infra, hospitality, Security,and event team.  
%}}
\section{Personal \& contact information}

%\cventry{}{Office contact information}{}{}{}{} 


\cventry{}{\textnormal{Gender: Male}}{}{}{}{}
\cventry{}{\textnormal{Birth date: Oct-16-1991}}{}{}{}{}
\cventry{}{\textnormal{Nationality: Chinese}}{}{}{}{}
\cventry{}{\textnormal{Email: \emailsymbol \emaillink{l.kong@uva.nl} ~~(or) ~~\emailsymbol \emaillink{lingweik6@gmail.com}}
}{}{}{}{}
\cventry{}{\textnormal{Mobile: \mobilesymbol{+31 (0)685438594}
}}{}{}{}{Nationally please call 0685438594;
Internationally please call 0031685438594 or +31685438594}
\cventry{}{\textnormal{Homepage: (\href{http://sites.google.com/view/lingwei-kong}{Google site}) http://sites.google.com/view/lingwei-kong
}}{}{}{}{(\href{https://lingwei-kong.github.io/}{or Git backup of  my website}) https://lingwei-kong.github.io/}

\vspace{1mm}

\cventry{}{\textnormal{Office: University of Amsterdam}}{}{office E3.26}{}{
	\textsc{Visiting Address: Room E3.26, Roetersstraat 11, 1018 WB Amsterdam} \\
\textsc{Postal Address:} \textsc{PO Box 15867, 1001 NJ Amsterdam, The Netherlands}}
\vspace{-2mm}
\section{References}
\cventry{}{\href{https://www.uva.nl/en/profile/k/l/f.r.kleibergen/f.r.kleibergen.html}{{{Professor F.R. (Frank) Kleibergen}}} (\textbf{main advisor}) }{}{University of Amsterdam}{}{\homepagesymbol\href{https://www.uva.nl/en/profile/k/l/f.r.kleibergen/f.r.kleibergen.html}{https://www.uva.nl/en/profile/k/l/f.r.kleibergen/f.r.kleibergen.html}\\
	 ~~~\emailsymbol \emaillink{F.R.Kleibergen@uva.nl}~~\phonesymbol{+31 (0)205254397}\\
\textsc{Address: Room E4.31, Roetersstraat 11, 1018 WB Amsterdam}}  
\vspace{1mm}

\cventry{}{\href{https://www.uva.nl/en/profile/b/o/h.p.boswijk/h.p.boswijk.html}{{Professor H.P. (Peter) Boswijk}}}{}{University of Amsterdam}{}{\homepagesymbol\href{https://www.uva.nl/en/profile/b/o/h.p.boswijk/h.p.boswijk.html}{https://www.uva.nl/en/profile/b/o/h.p.boswijk/h.p.boswijk.html}	\\\emailsymbol \emaillink{H.P.Boswijk@uva.nl}~~\phonesymbol{+31 (0)205254316; +31 (0)205254252}\\
	\textsc{Address: Room E4.30, Roetersstraat 11, 1018 WB Amsterdam}}  
\vspace{1mm}

\cventry{}{\href{https://sites.google.com/site/zhaoguozhan/home}{{Associate Professor Zhaoguo Zhan}}}{}{Kennesaw State University}{}{\homepagesymbol\href{https://sites.google.com/site/zhaoguozhan/home}{https://sites.google.com/site/zhaoguozhan/home} \\\emailsymbol \emaillink{zzhan@kennesaw.edu}~~\emailsymbol \emaillink  {zhaoguozhan@gmail.com}~~\phonesymbol{+1(470)578-6537}\\ \textsc{Address: 1000 Chastain Rd, Kennesaw, GA 30144, U.S.A.}
	}  

 
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------
\vspace{1mm}
\section{Education}
\cventry{2016 - }{\textnormal{Ph.D. in Economics}}{}{University of Amsterdam \& Tinbergen Institute}{}{
	Ph.D. Candidate in  Faculty of Economics and Business,
	Quantitative Economics section.\\
	\textnormal{Expected Completion Date: May 2020.}}
\vspace{1mm}
\cventry{2014 - 2016}{\textnormal{MPhil. in 		{Economics}}}{}{Tinbergen Institute}{}{with {\textbf{Distinction}}.}
\vspace{1mm}
\cventry{2012 - 2014}{\textnormal{Bachelor in Econometrics and Operations Research}}{}{University of Groningen}{}{with \textbf{Summa Cum Laude}. (Fudan-Groningen Double Degree Bachelor Joint Programme in Economics and Business Economics)}
\vspace{1mm}
\cventry{2010 - 2014}{\textnormal{Bachelor in  Mathematical Economics}}{}{Fudan University}{}{\textnormal{(Fudan-Groningen Double Degree Bachelor Joint Programme in Economics and Business Economics)}}




\section{Research \& Teaching Fields}
\cvitem{Research}{Econometric theory, particularly on weak identification problems and applications in asset pricing models}
\cvitem{Teaching}{Statistics, Measure theory, Econometrics (Time Series, Applied Financial Econometrics)}

%----------------------------------------------------------------------------------------
%	Masters SECTION
%----------------------------------------------------------------------------------------

%\section{Masters Thesis}

%\cvitem{Title}{\emph{Technologies and characterization of ferroelectric polymers for biomedical sensors}}
%\cvitem{Supervisors}{Professor Antonino Fiorillo}
%\cvitem{Description}{This thesis is based on the implementation of a temperature sensor.}
\vspace{1mm}
\section{Teaching Assistant \& Thesis Supervision}
%\cventry{}{University of Amsterdam}{}{}{}{}
\cventry{2019}{University of Amsterdam}{}{}{}{Advanced Econometrics I (Graduate);\\ Applied Financial Econometrics (Graduate);\\
Master Thesis Supervision (second reader)}
\vspace{1mm}
\cventry{2018}{University of Amsterdam}{}{}{}{Econometrics (Undergraduate); \\
	Advanced Econometrics I (Graduate); \\
	Bachelor's Thesis and Thesis Seminar Econometrics.}
\vspace{1mm}
%\cventry{}{}{}{}{}{}
\cventry{2015}{Tinbergen Institute}{}{}{}{Math II (Graduate);\\ Advanced Econometrics III (Graduate).} 
\vspace{1mm}

%\cventry{}{}{}{}{}{}

\cventry{2013 - 2014}{University of Groningen}{}{}{}{Probability Theory (Undergraduate); \\
probability Distribution (Undergraduate).}


\vspace{1mm}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Honours and Awards}
%\cventry{2018}{\textnormal{Econometric Game 2018 (Final round, team leader of UvA team)}}{}{}{}{}
\vspace{1mm}
\cventry{2014 - 2016}{\textnormal{Tinbergen Institute Full Scholarship}}{}{}{}{}
\vspace{1mm}
\cventry{2012 - 2014}{\textnormal{Scholarship of Fdu-Rug Double Major Program}}{}{}{}{}
\vspace{1mm}
\cventry{2012}{\textnormal{Scholarship for Outstanding Students (Fudan)}}{}{}{}{} 
\cventry{2011}{\textnormal{Scholarship of Shenmeihe (First Class)}}{}{}{}{}
\cventry{2010}{\textnormal{College Star of Tengfei (Fudan)}}{}{}{}{}
\vspace{1mm}
\section{Conferences \& Workshops}
\cventry{2021}{Presentation}{}{}{}{}
\cventry{2020}{Presentation}{}{}{}{19th Winter school on Mathematical Finance (Lunteren).}
\cventry{2019}{Presentation}{}{}{}{Econometric Society European Winter Meeting (Rotterdam); Asian Meeting of the Econometric Society (Xiamen).}
\cventry{}{Poster}{}{}{}{ Netherlands Econometric Study Group Conference (Amsterdam).}
\cventry{}{Attending}{}{}{}{Twelfth Annual SoFiE Asian Conference (Shanghai); Machine Learning for Economics and Econometrics(Rotterdam);  Econometric Institute International PhD Conference (Rotterdam).}

\vspace{1mm}
\cventry{2018}{Presentation}{}{}{}{QED Jamboree (Alicante)}
\cventry{}{Poster}{}{}{}{Netherlands Econometric Study Group Conference (Amsterdam).}
\cventry{}{Attending}{}{}{}{2018 SoFiE Summer School on Machine Learning and Empirical Asset Pricing (Chicago).}

\vspace{1mm}
\cventry{2017}{Attending}{}{}{}{28th (EC)2 Conference on Time-varying Parameter Models(Amsterdam); European Conference of Econometrics Community (Amsterdam); 12th Tinbergen Institute Conference: Inference Issues in Econometrics (Amsterdam); Rhenish Multivariate Time Series Econometrics (RMSE) Workshops (Rotterdam); 16th Winter school on Mathematical Finance (Lunteren)}

%\vspace{-1mm}
%\cventry{2016}{}{}{}{}{Research in Behavioral Finance Conference 2016 (Amsterdam); }




%------------------------------------------------


%----------------------------------------------------------------------------------------
%	Coursework SECTION
%----------------------------------------------------------------------------------------
\vspace{5mm}
\section{Research Papers}
\vspace{2mm}
\cventry{}{Weak (Proxy) Factors Robust Hansen-Jagannathan Distance For Linear Asset Pricing Models \textnormal{(Job Market Paper)}}{}{}{}{\vspace{.1em} * \hspace*{.5em}
	\textnormal{\indent \textbf{Abstract:} The Hansen-Jagannathan (HJ) distance statistic is one of the most dominant measures of model misspecification. However, the conventional HJ specification test procedure has poor finite sample performance, and we show that it can be size distorted even in large samples when (proxy) factors exhibit small correlations with asset returns. In other words, applied researchers are likely to reject a model even when it is correctly specified falsely. 
		We provide two alternatives for the HJ statistic and two corresponding novel procedures for model specification tests, which are robust against the presence of weak (proxy) factors, and we also offer a novel robust risk premia estimator. Simulation exercises support our theory. Our empirical application documents the non-reliability of the traditional HJ test as it may produce counter-intuitive results, when comparing nested models, by rejecting a four-factor model but not the reduced three-factor model, while our proposed methods are practically more appealing and show support for a four-factor model for Fama French portfolios.   }}
\vspace{8mm}
\cventry{}{Identification Robust Testing of Risk Premia in Finite Samples}{}{}{}{with F. Kleibergen, Z.Zhan.\\ \textit{Halbert White Jr. Memorial Lecture (Twelfth Annual SoFiE Asian Conference (Shanghai))}\\ \textit{Journal of Financial Econometrics (\textbf{conditionally accepted}).}\\~~ \\\vspace{.1em}* \hspace{.5em}
\textnormal{\textbf{Abstract:} The reliability of tests on the risk premia in linear factor models is threatened by
	limited sample sizes and weak identification of risk premia frequently encountered in
	applied work. We propose novel tests on the risk premia that are robust to both limited
	sample sizes and the identification strength of the risk premia as reflected by the quality
	of the risk factors. These tests are appealing for empirically relevant settings, and lead
	to confidence sets of risk premia that can substantially differ from conventional ones.
	To show the latter, we revisit two high-profile empirical applications.}}
\vspace{8mm}
\cventry{}{Weak (And Over) Identification In Affine Term Structure Models}{}{}{}{\vspace{.1em}* \hspace{.5em} \textnormal{\textbf{Abstract:} 	 Affine term structure models explore the factor structures in a set of bonds with various maturities. Tractability of affine models comes at the cost of restrictive structural assumptions, induced by the no-arbitrage requirement. Two main issues arise from these structural assumptions: weak identification due to small-$\beta$s factors, factors weakly correlated with returns and thus less informative for the identification, and misspecification due to the highly parametric setting.   
		We focus on the reduced rank restrictions in the form of $D=\beta \lambda_F$,
and investigate a regression-based estimator for a general class of affine term structure models. We show that statistical inference on the
		estimated risk premia based on the regression-based estimator might be misleading with small $\beta$s factors. We propose robust tests  against bad-behaved factors, and check the validity of reduced rank restrictions in the affine term
		structure models.}}
 
 \vspace{25mm}
 {\color{color2!50}\rule{\textwidth}{.25ex}}%
%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------
%\section{Extra Curricular}
%\cventry{26 Jan-2016}{Best Cadet Award, NCC}{-- Got best cadet award in institute's 50 members team of NCC }{}{}{}
%\vspace{-1mm}
%\cventry{Jan 2016}{Inter-hostel}{--1st runner up in 110m hurdle race, 2nd runner up in 100m and 400m race}{}{}{}
%\vspace{-1mm}
%\cventry{2015-16}{Directed and Acted}{in interhostel street-play competition on awareness topic "Akhir mardangi kyun?"}{}{}{}
%\vspace{-1mm}
%\cventry{April 2017}{Volunteer}{in Fourth Boeing IIT-National Aeromodelling Competition FINALS.}{}{}{}
%\vspace{-1mm}
%\cventry{2017-19}{Hostel maintenance}{--member of hostel maintenance committee in Gym room and mess}{}{}{}
%\section{Communication Skills}

%\cvitem{2010}{Oral Presentation at the California Business Conference}
%\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

% \section{Interests}

% \renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
% \cvlistdoubleitem{Piano}{}
% \cvlistitem{Baseball}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}



